Evaluating infectious disease forecasts with allocation scoring rules

### 2023-09-03 alloscore_manuscript/alloscore-application.Rnw
change allocation problem def in step 3

\paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} The Bayes act associated with the forecast, $x^{F,K}$, is the allocation that minimizes the expected loss:
\begin{align}
    x^{F,K} &= \underset{0 \leq x}{\mathrm{arg min}}\,\, \mathbb{E}_{F} [s_A(x, Y)] \text{ subject to }
     \, \sum_{i=1}^N x_i = K, \label{AP}
\end{align}
where $\mathbb{E}_{F} [s_A(x, Y)] = \sum_{i=1}^{N} L \mathbb{E}_{F_i}[\max(0, Y_i - x_i)]$ sums the expected loss due to unmet need across all locations.

In the supplement we show that for a typical forecast $F$ and constraint level $K$, the components $x_i^{F,K}$ of the Bayes act are quantiles 
$q_{i,\tau} = F_i^{-1}(\tau)$ of the marginal forecasts $F_i$ for a probability level $\tau = \tau(K,F)$ satisfying the equation
\begin{align}
\sum_{i=1}^{N}q_{i,\tau} = K.
\end{align}
We note that $\tau(K,F)$ depends not only on the constraint level $K$ defining the decision problem but also on the forecast $F$. This is quite
different from the situation for quantile scores and the WIS, where the probability levels used to calculate scores are fixed.

>>>>

\paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} The Bayes act associated with the forecast, $x^{F,K}$, is the allocation that minimizes the expected loss, that is, the solution of the \emph{allocation problem} associated with $K$
\begin{align}
    \underset{0 \leq x}{\mathrm{minimize}}\,\, \mathbb{E}_{F} [s_A(x, Y)] \text{ subject to }
     \, \sum_{i=1}^N x_i = K, \label{AP}
\end{align}
where $\mathbb{E}_{F} [s_A(x, Y)] = \sum_{i=1}^{N} L \mathbb{E}_{F_i}[\max(0, Y_i - x_i)]$ sums the expected loss due to unmet need across all locations.

In the supplement we show that for a typical forecast $F$ and constraint level $K$, the components $x_i^{F,K}$ of the Bayes act are quantiles 
$q_{i,\tau} = F_i^{-1}(\tau)$ of the marginal forecasts $F_i$ for a probability level $\tau = \tau(K,F)$ that is defined by the constraint equation of the
allocation problem
\begin{align}
\sum_{i=1}^{N}q_{i,\tau} = K.
\end{align}
We note that $\tau(K,F)$ depends not only on the constraint level $K$ defining the decision problem but also on the forecast $F$. This is quite
different from the situation for quantile scores and the WIS, where the probability levels used to calculate scores are fixed.
